---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r}
library(igraph)
library(tidyverse)
library(questionr)
```

### Read data file
```{r}
#read file in as members
mt_edgelist <- read.csv("../data cleaning/all-data.csv")

View(mt_edgelist)
head(mt_edgelist)
```
Note: the sender is in the first column and receiver in the second

```{r}
people <- filter(mt_edgelist, sourcetweet_type == "quoted" | is.na(sourcetweet_type))
print(unique(people$user_username))

```


```{r}
#Careful, this overcounts!  The 'text' field is truncated for retweets, need to load
#new data file that includes sourcetweet_text field
JointMath<-mt_edgelist[mt_edgelist$user_username == 'JointMath',]
#did not use any of the hashtags or did not include a @JointMath tag
NotHT20<-subset(JointMath, !grepl("#JMM2020", JointMath$sourcetweet_text ), )
NotHT<-subset(NotHT20, !grepl("#JMM2021", NotHT20$sourcetweet_text ), )
Notpinged<-subset(NotHT, !grepl("@JointMath", NotHT$sourcetweet_text ))

# for example - this has nothing that says RT me...
Notpinged$text[12]
Notpinged
```

Clearly the JointMath handle was RTing JMM tweets



# What are our top group tweeting about?
```{r}
influencer_names = c("WanderingPoint","mathprofcarrie","sbagley","pwr2dppl","RG1gal","LoboWithACause","VictorPiercey1")
#influencers <- filter(mt_edgelist, user_username %in% influencer_names)

codes <- colnames(mt_edgelist)[54:88]

for (person in influencer_names) {
  influencers <- filter(mt_edgelist, user_username == person)
  #Drop retweets
  influencersOTQT <- filter(influencers, sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  
  n=nrow(influencersOTQT)
  influencer_tweets <- c()
  cnames <- c()
  for (code in codes) {
    freq=length(which(influencersOTQT[code]=="True"))/n
    if (freq>0){ 
      influencer_tweets <- append(influencer_tweets,freq)
      cnames <- append(cnames,code)}
  }

names(influencer_tweets) <- cnames
influencer_tweets <- sort(influencer_tweets,decreasing=TRUE)
print(person)
print(n)
print(knitr::kable(influencer_tweets))
cat("\n\n")
}
```

# Distribution of SJEDI and CC Math codes for top tweeters
```{r}
top_people = data.frame( name= c("WanderingPoint","mathprofcarrie","sbagley","pwr2dppl","LoboWithACause","VictorPiercey1"))
#influencers <- filter(mt_edgelist, user_username %in% influencer_names)
print(top_people)

codes <- c("representation","lbgtq","bipoc","gender","indigenous","power","advocacy","learning","economic","SJEDI.impact")
#,"humanize","jmm.experience","math.experience","futures","math.practice","current.events","allyship.in.math","CC.impact")

for (code in codes) {
  column = c()
  for (person in top_people$name){
   influencers <- filter(filter(mt_edgelist, user_username == person), sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  #Drop retweets
#   influencersOTQT <- filter(influencers, sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  
  n=nrow(influencers)
  freq=length(which(influencers[[code]]=="True"))/n
  column <- append(column,freq)
  }

  top_people[[code]] <- column
}
 
#num=c() 
#for (person in top_people$name){
#   num <- append(num, nrow(filter(filter(mt_edgelist, user_username == person), sourcetweet_type == "quoted" | is.na(sourcetweet_type))))
#}
#top_people$n <- num

#print(top_people)


top_people %>% 
  pivot_longer(cols = codes, names_to="code") %>%
  ggplot(aes(code, value, fill = name)) +
  geom_col(position = position_dodge(), color = "black") +
  #scale_alpha_manual(values = c(0.5, 1), guide = guide_none()) +
  facet_grid(~code, scales = "free_x", switch = "x") +
  theme(strip.placement  = "outside",
        panel.spacing    = unit(0, "points"),
        strip.background = element_blank(),
        axis.text.x=element_blank(), 
        strip.text.x = element_text(angle = 90)
      #axis.ticks.x=element_blank()
        ) +
        #strip.text       = element_text(face = "bold", size = 12)) +
  labs(x = "Codes in SJEDI Theme",y="Frequency")

```
```{r}
top_people = data.frame( name= c("WanderingPoint","mathprofcarrie","sbagley","pwr2dppl","LoboWithACause","VictorPiercey1"))
#influencers <- filter(mt_edgelist, user_username %in% influencer_names)
print(top_people)

#codes <- c("representation","lbgtq","bipoc","gender","indigenous","power","advocacy","learning","economic","SJEDI.impact")
codes <- c("humanize","jmm.experience","math.experience","futures","math.practice","current.events","allyship.in.math","CC.impact")

for (code in codes) {
  column = c()
  for (person in top_people$name){
   influencers <- filter(filter(mt_edgelist, user_username == person), sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  #Drop retweets
#   influencersOTQT <- filter(influencers, sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  
  n=nrow(influencers)
  freq=length(which(influencers[[code]]=="True"))/n
  column <- append(column,freq)
  }

  top_people[[code]] <- column
}
 
#num=c() 
#for (person in top_people$name){
#   num <- append(num, nrow(filter(filter(mt_edgelist, user_username == person), sourcetweet_type == "quoted" | is.na(sourcetweet_type))))
#}
#top_people$n <- num

#print(top_people)


top_people %>% 
  pivot_longer(cols = codes, names_to="code") %>%
  ggplot(aes(code, value, fill = name)) +
  geom_col(position = position_dodge(), color = "black") +
  #scale_alpha_manual(values = c(0.5, 1), guide = guide_none()) +
  facet_grid(~code, scales = "free_x", switch = "x") +
  theme(strip.placement  = "outside",
        panel.spacing    = unit(0, "points"),
        strip.background = element_blank(),
        axis.text.x=element_blank(), 
        strip.text.x = element_text(angle = 90)
      #axis.ticks.x=element_blank()
        ) +
        #strip.text       = element_text(face = "bold", size = 12)) +
  labs(x = "Codes in Creating Change Theme",y="Frequency")

```

# What are our netweavers tweeting about?
```{r}
influencer_names = c("mathprofcarrie","JointMath","pwr2dppl","LoboWithACause","sbagley")
#influencers <- filter(mt_edgelist, user_username %in% influencer_names)

codes <- colnames(mt_edgelist)[54:88]

for (person in influencer_names) {
  influencers <- filter(mt_edgelist, user_username == person)
  #Drop retweets
  #influencersOTQT <- filter(influencers, sourcetweet_type == "quoted" | is.na(sourcetweet_type))
  
  n=nrow(influencers)
  influencer_tweets <- c()
  cnames <- c()
  for (code in codes) {
    freq=length(which(influencers[code]=="True"))/n
    if (freq>0){ 
      influencer_tweets <- append(influencer_tweets,freq)
      cnames <- append(cnames,code)}
  }

names(influencer_tweets) <- cnames
influencer_tweets <- sort(influencer_tweets,decreasing=TRUE)
print(person)
print(n)
print(knitr::kable(influencer_tweets))
cat("\n\n")
}
```


```{r}
#What was @JointMath tweeting about?
jointmath <- filter(mt_edgelist, user_username == "JointMath")
n=nrow(jointmath)
codes <- colnames(jointmath)[54:88]
joint_tweets <- c()
for (code in codes) {
  joint_tweets <- append(joint_tweets, length(which(jointmath[code]=="True"))/n)
}
names(joint_tweets) <- codes
joint_tweets <- sort(joint_tweets,decreasing=TRUE)
print(joint_tweets)
print(n)
```

# Who is tweeting about important things?
```{r}
#important_codes <- c("representation","gender","indigenous","advocacy","power","bipoc")
#
#for (code in important_codes){
#  code_only <- filter(mt_edgelist, (!!as.symbol(code))=="True")
#  print(code)
#  top_tweeters=sort(table(code_only$user_username),decreasing=TRUE)
  #print(head(top_tweeters,10))
#  barplot(head(top_tweeters,10),las=2)
#}

```

# Who is tweeting about SJEDI and CC in Math?
```{r}
themes=c("SJEDI","Creating.change.in.math", "Building.community", "Broadening.the.counterpublic", "Self.organization")
for (theme in themes){
print(theme)
code_only <- filter(filter(mt_edgelist, (!!as.symbol(theme))==1), sourcetweet_type == "quoted" | is.na(sourcetweet_type))
top_tweeters=sort(wtd.table(x=code_only$user_username, weights=1+code_only$retweet_count+code_only$quote_count),decreasing=TRUE)
barplot(head(top_tweeters,10),las=2)
}
```
# Who is tweeting about SJEDI and CC in Math? unweighted version
```{r}
themes=c("SJEDI","Creating.change.in.math", "Building.community", "Broadening.the.counterpublic", "Self.organization")
for (theme in themes){
print(theme)
code_only <- filter(filter(mt_edgelist, (!!as.symbol(theme))==1), sourcetweet_type == "quoted" | is.na(sourcetweet_type))
#top_tweeters=sort(wtd.table(x=code_only$user_username, weights=1+code_only$retweet_count+code_only$quote_count),decreasing=TRUE)
 top_tweeters=sort(table(code_only$user_username),decreasing=TRUE)
barplot(head(top_tweeters,10),las=2)
}
```

# Can we do code level too?

```{r}
codes <- colnames(mt_edgelist)[54:88]
for (code in codes){
print(code)
code_only <- filter(filter(mt_edgelist, (!!as.symbol(code))=="True"), sourcetweet_type == "quoted" | is.na(sourcetweet_type))

#Weighted
#top_tweeters=sort(wtd.table(x=code_only$user_username, weights=1+code_only$retweet_count+code_only$quote_count),decreasing=TRUE)

#Unweighted
top_tweeters=sort(table(code_only$user_username),decreasing=TRUE)

barplot(head(top_tweeters,5),las=2)
}
```