---
title: "codebreaks"
author: "Carrie Diaz Eaton"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(splitstackshape) 
library(reshape2)
library(ggplot2)
library(forcats)
```

## Just with SJEDI codes for now
# run the Code Analysis Rmd first to get the variables in the environment

```{r}
# flatten across ;
# this will create a separate column for each code
# unfortunately the "long" version is not working
SJEDI.codes<-cSplit(SJtweets, 'SJEDI.code', sep=";", direction = "wide", type.convert = FALSE)
View(SJEDI.codes)
```

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
code.columns<-colnames(SJEDI.codes)[grepl("SJEDI.code",colnames(SJEDI.codes))]
just.codes<-select(SJEDI.codes,code.columns)
just.codes<-cbind(X = SJEDI.codes$X,just.codes)
long.codes<-melt(just.codes, id = "X", value.name = "SJEDI.code", na.rm = TRUE)

```

## Summarize data
```{r}
SJEDI.counts <- long.codes %>% count(SJEDI.code)
print(SJEDI.counts)
```

## Fix data mistypes
```{r}
long.codes[long.codes == "indigneous"] <- "indigenous"
long.codes[long.codes == "lgbtq"] <- "lgbtq+"
long.codes[long.codes == "lgtbq+"] <- "lgbtq+"
long.codes[long.codes == "represenation"] <- "representation"
long.codes[long.codes == "SJEDI Impact"] <- "SJEDI impact"

#then look again to make sure
SJEDI.counts <- long.codes %>% count(SJEDI.code)
print(SJEDI.counts)
```


## Visualize
```{r}
# Barplot
ggplot(SJEDI.counts, aes(x=SJEDI.code, y = n)) + 
  geom_bar(stat = "identity") +
  coord_flip()

```

## Ordered version
```{r}
# prep to save as jpg
jpeg('SJEDIplot.jpg')

# Reorder following the value of another column:
SJEDIplot<- SJEDI.counts %>%
  mutate(name = fct_reorder(SJEDI.code, n)) %>%
  ggplot(aes(x=name, y = n)) +
    geom_bar(stat="identity") +
    coord_flip() +
    xlab("") +
    theme_bw()

#turn off plot writing
dev.off()

SJEDIplot
```



## Building Community

```{r}
# flatten across ;
# this will create a separate column for each code
# unfortunately the "long" version is not working
BC.codes<-cSplit(BCtweets, 'BC.code', sep=";", direction = "wide", type.convert = FALSE)
View(BC.codes)
```

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
code.columns<-colnames(BC.codes)[grepl("BC.code",colnames(BC.codes))]
just.codes<-select(BC.codes,code.columns)
just.codes<-cbind(X = BC.codes$X,just.codes)
long.codes<-melt(just.codes, id = "X", value.name = "BC.code", na.rm = TRUE)

```

## Summarize data
```{r}
BC.counts <- long.codes %>% count(BC.code)
print(BC.counts)
```

## Fix data mistypes
```{r}
long.codes[long.codes == "emotional suport"] <- "emotional support"
long.codes[long.codes == "talk suport"] <- "talk support"
long.codes[long.codes == "BC Impact"] <- "BC impact"

#then look again to make sure
BC.counts <- long.codes %>% count(BC.code)
print(BC.counts)
```


## Visualize
```{r}
# Make
# Barplot
ggplot(BC.counts, aes(x=BC.code, y = n)) + 
  geom_bar(stat = "identity") +
  coord_flip()

```

## Ordered version
```{r}
# prep to save as jpg
jpeg('BCplot.jpg')

# Reorder following the value of another column:
BCplot<- BC.counts %>%
  mutate(name = fct_reorder(BC.code, n)) %>%
  ggplot(aes(x=name, y = n)) +
    geom_bar(stat="identity") +
    coord_flip() +
    xlab("") +
    theme_bw()

#turn off plot writing
dev.off()

BCplot
```



## Broadening the Conversation

```{r}
# flatten across ;
# this will create a separate column for each code
# unfortunately the "long" version is not working
BtC.codes<-cSplit(BtCtweets, 'BtC.code', sep=";", direction = "wide", type.convert = FALSE)
View(BtC.codes)
```

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
code.columns<-colnames(BtC.codes)[grepl("BtC.code",colnames(BtC.codes))]
just.codes<-select(BtC.codes,code.columns)
just.codes<-cbind(X = BtC.codes$X,just.codes)
long.codes<-melt(just.codes, id = "X", value.name = "BtC.code", na.rm = TRUE)

```

## Summarize data
```{r}
BtC.counts <- long.codes %>% count(BtC.code)
print(BtC.counts)
```

## Fix data mistypes
```{r}
long.codes[long.codes == "influencer"] <- "influencers"
long.codes[long.codes == "hashtag"] <- "hashtags"

#then look again to make sure
BtC.counts <- long.codes %>% count(BtC.code)
print(BtC.counts)
```


## Visualize
```{r}
# Make
# Barplot
ggplot(BC.counts, aes(x=BC.code, y = n)) + 
  geom_bar(stat = "identity") +
  coord_flip()

```

## Ordered version
```{r}
# prep to save as jpg
jpeg('BtCplot.jpg')

# Reorder following the value of another column:
BtCplot<- BtC.counts %>%
  mutate(name = fct_reorder(BtC.code, n)) %>%
  ggplot(aes(x=name, y = n)) +
    geom_bar(stat="identity") +
    coord_flip() +
    xlab("") +
    theme_bw()

#turn off plot writing
dev.off()

BtCplot
```

## Creating Change in Math

```{r}
# flatten across ;
# this will create a separate column for each code
# unfortunately the "long" version is not working
CCM.codes<-cSplit(CCtweets, 'CCM.code', sep=";", direction = "wide", type.convert = FALSE)
View(CCM.codes)
```

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
code.columns<-colnames(CCM.codes)[grepl("CCM.code",colnames(CCM.codes))]
just.codes<-select(CCM.codes,code.columns)
just.codes<-cbind(X = CCM.codes$X,just.codes)
long.codes<-melt(just.codes, id = "X", value.name = "CCM.code", na.rm = TRUE)

```

## Summarize data
```{r}
CCM.counts <- long.codes %>% count(CCM.code)
print(CCM.counts)
```

## Fix data mistypes
```{r}
long.codes[long.codes == "humamize"] <- "humanize"
long.codes[long.codes == "jmm experiences"] <- "jmm experience"
long.codes[long.codes == "math experiences"] <- "math experience"
long.codes[long.codes == "math practice"] <- "math practices"

#then look again to make sure
CCM.counts <- long.codes %>% count(CCM.code)
print(CCM.counts)
```


## Visualize
```{r}
## Ordered version of barplot

# prep to save as jpg
jpeg('CCMplot.jpg')

# Reorder following the value of another column:
CCMplot<- CCM.counts %>%
  mutate(name = fct_reorder(CCM.code, n)) %>%
  ggplot(aes(x=name, y = n)) +
    geom_bar(stat="identity") +
    coord_flip() +
    xlab("") +
    theme_bw()

#turn off plot writing
dev.off()

CCMplot
```



## Self-Organization

```{r}
# flatten across ;
# this will create a separate column for each code
# unfortunately the "long" version is not working
SO.codes<-cSplit(SOtweets, 'SO.code', sep=";", direction = "wide", type.convert = FALSE)
View(SO.codes)
```

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
code.columns<-colnames(SO.codes)[grepl("SO.code",colnames(SO.codes))]
just.codes<-select(SO.codes,code.columns)
just.codes<-cbind(X = SO.codes$X,just.codes)
long.codes<-melt(just.codes, id = "X", value.name = "SO.code", na.rm = TRUE)

```

## Summarize data
```{r}
SO.counts <- long.codes %>% count(SO.code)
print(SO.counts)
```

## Fix data mistypes
```{r}
long.codes[long.codes == "so impact"] <- "SO impact"
long.codes[long.codes == "SO Impact"] <- "talk support"
long.codes[long.codes == "strategic plannin"] <- "strategic planning"
long.codes[long.codes == "strategic pplanning"] <- "strategic planning"

#then look again to make sure
SO.counts <- long.codes %>% count(SO.code)
print(SO.counts)
```


## Visualize
```{r}
# Ordered version

# prep to save as jpg
jpeg('SOplot.jpg')

# Reorder following the value of another column:
SOplot<- SO.counts %>%
  mutate(name = fct_reorder(SO.code, n)) %>%
  ggplot(aes(x=name, y = n)) +
    geom_bar(stat="identity") +
    coord_flip() +
    xlab("") +
    theme_bw()

#turn off plot writing
dev.off()

BCplot
```




## All codes

```{r}
# manually create long version
# but to simplify, I'm only keeping the tweet # X column
colnames(SJEDI.counts)[1]<-"code" 
colnames(BC.counts)[1]<-"code" 
colnames(BtC.counts)[1]<-"code" 
colnames(CCM.counts)[1]<-"code" 
colnames(SO.counts)[1]<-"code" 

all.codes <- bind_rows("SJEDI" = SJEDI.counts, "BC" = BC.counts, "BtC" = BtC.counts, "CCM" = CCM.counts, "SO" = SO.counts, .id = "Bucket")

print(all.codes)

```


## Visualize
```{r}
# Ordered version

# prep to save as jpg
jpeg('allcodesplot.jpg')

# Reorder following the value of another column:
allcodesplot<- ggplot(all.codes, aes(x=code, y = n)) +
    geom_bar(stat="identity") +
    coord_flip()

#turn off plot writing
dev.off()

allcodesplot
```




