---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
## Mise en place - Getting your workspace ready

Load the igraph package
```{r}
# load igraph
library(igraph)
library(centiserve)
library(tidyverse)
```

# Create Graph Object
## This is the twitter network of users. Users are connected if there RT or reply or a quote tweet.

### Read data file
```{r}
#read file in as members
mt_edgelist <- read.csv("../data cleaning/people-edge-list.csv")
View(mt_edgelist)
head(mt_edgelist)
```
Note: the sender is in the first column and receiver in the second

```{r}
#create a matrix, just of Sender and Receiver
send_interact <- cbind(Sender = mt_edgelist$Sender,Interactor = mt_edgelist$Receiver)

# check it out
head(send_interact)
dim(send_interact)
```

### Define network from edgelist
```{r}
# make a graph object
mathpeeps.g <- graph.edgelist(send_interact, directed = TRUE)
```


### Visualize the group network
Use the igraph documentation @igraph to comment what the code below is doing:

* [layout_with_fr]{https://igraph.org/r/doc/layout_with_fr.html}  
* [edge_attr]{https://igraph.org/r/doc/edge_attr.html}  Then run the following code & revise your code as necessary.  

```{r}
#plot features
la <- layout_with_fr(mathpeeps.g)
e.wt <- edge_attr(mathpeeps.g, "weight")

#plot group network
plot(mathpeeps.g, layout=la, vertex.size=10,edge.width=e.wt,vertex.label=V(mathpeeps.g)$name, edge.arrow.size = .2)
```
```{r}
png("people.png", width = 465, height = 225, units='mm', res = 300)
plot(mathpeeps.g, layout=la, vertex.size=2,edge.width=e.wt,vertex.label=V(mathpeeps.g)$name, edge.arrow.size = .2)
dev.off()
```


### Network Statistics

Degree exploration
```{r}
#Degree of top 10 in order
deg.peeps <- degree(mathpeeps.g,  mode = "all",
  loops = FALSE,
  normalized = FALSE)
names(deg.peeps) <- V(mathpeeps.g)$name
ind <- order(-deg.peeps)
deg.peeps[ind][1:10]

#Degree of top 10 in order
indeg.peeps <- degree(mathpeeps.g,  mode = "in",
  loops = FALSE,
  normalized = FALSE)
names(indeg.peeps) <- V(mathpeeps.g)$name
ind <- order(-indeg.peeps)
indeg.peeps[ind][1:10]

#Out degree of top 10 in order
outdeg.peeps <- degree(mathpeeps.g,  mode = "out",
  loops = FALSE,
  normalized = FALSE)
names(outdeg.peeps) <- V(mathpeeps.g)$name
ind <- order(-outdeg.peeps)
outdeg.peeps[ind][1:10]

```

The high degree of RG1gal comes from people mentioning her, which makes sense - one of the most frequently used codes was around humanizing & so she was tagged/replied to multiple times [38], but only tweeted 2x.

Interesting that JointMath has the second highest Twitter outdegree. Do they autoretweet everything that they are tagged in?
```{r}
JointMath<-mt_edgelist[mt_edgelist$Sender == 'JointMath',]
#did not use any of the hashtags or did not include a @JointMath tag
NotHT20<-subset(JointMath, !grepl("#JMM2020", JointMath$text ), )
NotHT<-subset(NotHT20, !grepl("#JMM2021", NotHT20$text ), )
Notpinged<-subset(NotHT, !grepl("@JointMath", NotHT$text ))

# for example - this has nothing that says RT me...
Notpinged$text[12]
```

Clearly the JointMath handle was RTing JMM tweets

```{r}
#Betweenness of top 10 in order
btwn.peeps <- betweenness(mathpeeps.g)
names(btwn.peeps) <- V(mathpeeps.g)$name
ind <- order(-btwn.peeps)
btwn.peeps[ind][1:10]

# katz centrality is like
#eigenvector centrality for directed graphs
#of top 10, but won't work if you have self-referential loops
#cent.eig <- katzcent(mathpeeps.g)
#names(cent.eig$vector) <- V(mathpeeps.g)$name
#ind <- order(-cent.eig$vector)
#cent.eig$vector[ind][1:10]

``` 

# What are important peeps tweeting about?
```{r}
#I think outdeg is what we want? But easy enough to tweak
influencer_names = names(outdeg.peeps[ind][1:10])
print(influencer_names)
influencers <- filter(mt_edgelist, Sender %in% influencer_names)
n=nrow(influencers)
codes <- colnames(influencers)[11:45]
print(codes)
influencer_tweets <- c()
for (code in codes) {
  #print(code)
  #print(length(which(influencers[code] == "True")))
  influencer_tweets <- append(influencer_tweets, length(which(influencers[code]=="True"))/n)
}
names(influencer_tweets) <- codes
influencer_tweets <- sort(influencer_tweets,decreasing=TRUE)
print(influencer_tweets)
```

# Active Tweeters
What were active tweeters doing. If you didn't just RT things other people wrote. What were you talking about?
```{r}
#Remove everyone with indegree 0
#this removes RT and QT that no one else enaged with
active.peeps<-subset(indeg.peeps, !grepl(0,indeg.peeps))
#subset just these in the full data
active.edgelist <- subset(mt_edgelist, grepl(paste(names(active.peeps), collapse='|'), mt_edgelist$Receiver))
```

##Define network
```{r}
#create a matrix, just of Sender and Receiver
active.send_interact <- cbind(Sender = active.edgelist$Sender,Interactor = active.edgelist$Receiver)

# check it out
head(active.send_interact)
dim(active.send_interact)
```

### Define network from edgelist
```{r}
# make a graph object
activepeeps.g <- graph.edgelist(active.send_interact, directed = TRUE)
```


### Visualize the group network

```{r}
#plot features
la <- layout_with_fr(activepeeps.g)
e.wt <- edge_attr(activepeeps.g, "weight")

#plot group network
plot(activepeeps.g, layout=la, vertex.size=10,edge.width=e.wt,vertex.label=V(activepeeps.g)$name, edge.arrow.size = .2)
```
```{r}
png("activepeople.png", width = 600, height = 600, units='mm', res = 600)
plot(activepeeps.g, layout=la, vertex.size=2,edge.width=e.wt,vertex.label=V(activepeeps.g)$name, edge.arrow.size = .2)
dev.off()
```

From this it seems like there are several people who are very well connected to each other (e.g. JointMath, pwr2dppl). Then there are people who are recruiting participation from outside the large interior cluster, engaging new networks (e.g. WanderingPoint, RG1gal, mathprofcarrie).  Is this how this plays out in the modularity clusters?



# Modularity
```{r}
#modularity 0.1105  37 communities
wtc<-cluster_walktrap(mathpeeps.g)
#membership(wtc)
modularity(mathpeeps.g, membership(wtc))

#takes a while to run
#optc<-optimal.community(mathpeeps.g)

#gives like 312 communities with modularity 0.0637
#ceb <-edge.betweenness.community(mathpeeps.g, directed= TRUE)
#membership(ceb)
#modularity(mathpeeps.g, membership(ceb))

#gives 259 communities with a modularity of 0.0192
#lpc<-label.propagation.community(mathpeeps.g)
#membership(lpc)
#modularity(mathpeeps.g, membership(lpc))

#gives 10 communities with a modularity of 0.065
# this gives almost the same value as the 213 communities, 
# but makes a lot more sense
infoc<-infomap.community(mathpeeps.g)
#membership(infoc)
modularity(mathpeeps.g, membership(infoc))

#connected components - 3 connected components
# modularity 0.0083
#compc<-components(mathpeeps.g)
#membership(compc)
#modularity(mathpeeps.g, membership(compc))


```